---
title: "Djouroutou Analysis and Figures "
author: "Jonathan S. Reeves"
date: "2023-05-25"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(car)
library(MASS)
library(performance)
library(ggplot2,verbose = FALSE)
library(ggnewscale)
library(cowplot)
library(dplyr,verbose = FALSE)
library(tidyr)
library(terra)
library(raster, verbose = FALSE)
library(sf)
library(tidyterra)
library(ggspatial)
library(ggpubr)

```


```{r DJR load_workspace}

load("../Data/DJR_Workspace.Rdata")

```

#Figure 1


##A
```{r Fig1.A , fig.height=6, fig.width=12, include= TRUE}

nut_colors <- c("#C41212","#30424D", "#7D6161", "#D1C700")


Fig1a <- base +
  new_scale_fill()+
  geom_sf(data = ntrees,
          aes(fill = species, shape = species), 
          shape = 21,
          size = 3.5,
          show.legend = FALSE, 
          inherit.aes = FALSE)+
  scale_fill_manual(values=nut_colors,
                    name = "Nut Species")+ 
  annotation_scale(location = "br", 
                   pad_x = unit(0.65, "cm"),
                   pad_y = unit(0.75, "cm"))+
  annotation_north_arrow(location = "br", 
                   pad_x = unit(0.7, "cm"),
                   pad_y = unit(1.2, "cm"),
                   style = north_arrow_orienteering())+
  annotate("text", x = 697000,y = 601000, label = "A.", size = 10)+
  theme_minimal() + 
  theme(legend.position = c(.84, .77),
        legend.key.height = unit(.5, 'cm'), 
        legend.background = element_rect(color = "black", fill = alpha("white", .75)),
        axis.title = element_blank(),
        axis.text = element_blank(), 
        panel.grid = element_blank(),
        panel.border = element_rect(fill =NA))


```

##B

```{r fig1.B}

Fig1b <- base + 
  guides(fill="none")+
  new_scale_fill()+
  geom_sf(data = ntrees,
          aes(fill = species, shape = species),
          alpha = 0,
          shape = 21,
          size = 3.5,
          show.legend = FALSE, 
          inherit.aes = FALSE)+
  stat_ellipse(data = ntrees,
               aes(x=X, y=Y,fill = species), 
               color = "black",
               alpha = .70 , 
               level = .65, 
               geom = "polygon", 
               type = 'norm',
               inherit.aes = FALSE) +
  scale_color_manual(values = nut_colors) +
  scale_fill_manual(values=nut_colors,
                    name = "Nut Species",
                    labels = c("Coula",
                               "Panda",
                               "Parinari",
                               "Saccoglotis"))+ 
  annotation_scale(location = "br", 
                   pad_x = unit(0.65, "cm"),
                   pad_y = unit(0.75, "cm"))+
  annotation_north_arrow(location = "br", 
                   pad_x = unit(0.7, "cm"),
                   pad_y = unit(1.2, "cm"),
                   style = north_arrow_orienteering())+
  annotate("text", x = 697000,y = 601000, label = "B.", size = 10)+
  theme_minimal() + 
  theme(legend.position = c(.80, .80),
        legend.key.height = unit(.5, 'cm'), 
        legend.background = element_rect(color = "black", fill = alpha("white", .75)),
        axis.title = element_blank(),
        axis.text = element_blank(), 
        panel.grid = element_blank(),
        panel.border = element_rect(fill =NA))

```

##C

```{r Fig1.C}

Fig1c <- ggplot(ntrees, aes(x = species, y = z)) + 
  geom_boxplot(aes(fill = species), show.legend = FALSE) +
  labs(x= "Species", y= "Elevation (m)") + 
  scale_fill_manual(values = nut_colors) + 
  annotate("text", x = .65,y = 181.25, label = "C.", size = 10)+
  theme(panel.border = element_rect(fill = NA,color = "black"),
  panel.background = element_blank())

```

### Final Fig 1
```{r Final Fig1, fig.height= 7, fig.width= 14}

fig1 <- egg::ggarrange(Fig1a, Fig1b,Fig1c, ncol = 3)
fig1
```

# SOM Figure 3: Rebound Hardness

```{r SOM.Fig.3}

djr_rbh_sum <- djr_rbh %>%
  group_by(Material) %>%
  summarise(min = round(min(Hardness_Value),2),
            mean = round(mean(Hardness_Value), 2),
            max = round(max(Hardness_Value), 2),
            sd = round(sd(Hardness_Value),2))


rock_colors <- rock_colors <- c("#F2F2F2", "#7B6823","#212A33", "#535353")
djr_rbh$Material <- factor(djr_rbh$Material,
                           levels = c("Quartz", "Diorite", "Granite"))  

SOM_Fig_3 <- ggplot(djr_rbh, aes(x = Material, y = Hardness_Value)) + 
  geom_boxplot(aes(fill = Material), show.legend = FALSE) + 
  labs(x = "Rock Type", y = "Rebound Hardness") + 
  scale_fill_manual(values = rock_colors)+
  theme(panel.background = element_rect(fill = NA, colour = "black"))




SOM_Fig_3
```

# Figure 2

## A
```{r fig2.A, fig.height=5,fig.width=5}

st_crs(qplots_djr_agg) <- "EPSG:32629"
qplots_djr_agg <- sf::st_crop(qplots_djr_agg, ntrees)
qplots_djr_agg <- qplots_djr_agg[!is.na(qplots_djr_agg$stone_material_recovered),,]

rock_colors <- c("#F2F2F2", "#7B6823","#212A33", "#535353")

Fig2a <- base + 
  new_scale_fill()+
  geom_sf(data = qplots_djr_agg,
          aes(fill = stone_material_recovered, size = n_stone, shape = stone_material_recovered),
          color = "black",
          alpha = .75, 
          inherit.aes = FALSE) + 
  scale_shape_manual(values = c(21,22,23,24)) +
  scale_fill_manual(values = rock_colors, guide = "none")+
  scale_size(range = c(4,8),
             breaks = c(1,3,5,7)) +
  labs(size = "N stones",
       shape = "Rock Type")+
  scale_y_continuous(limits = c(596400-300, 599268 + 700))+
  scale_x_continuous(limits = c(697046-100, 700829 + 300))+
  annotate("text", x = 697225,y = 599750, label = "A.", size = 10)+
  theme_minimal() + 
  theme(legend.position = "none",
        legend.direction = "vertical",
        legend.box = "horizontal",
        legend.key.height = unit(.5, 'cm'), 
        legend.background = element_rect(color = "black",
                                         fill = alpha("white", .75)),
        axis.title = element_blank(),
        axis.text = element_blank(), 
        panel.grid = element_blank(),
        panel.border = element_rect(fill =NA))


Fig2a_leg <- as_ggplot(get_legend(Fig2a + theme(legend.position = "top")))
```

## B

```{r Fig2.b}

Fig2b <- base +
  guides(fill="none")+
  geom_point(data = assemblages, aes(x = Easting, y = Northing, size = n_stone_no_anvil, shape = stone_anvil_present, color = primary_rm), inherit.aes = FALSE) +
  scale_color_manual(values = rock_colors) + 
  scale_size(range = c(2,8)) +
  coord_equal()+
  labs(color = "Primary RM",
       shape = "Stone Anvil",
       size = "N Stones")+
  scale_y_continuous(limits = c(596400-300, 599268 + 700))+
  scale_x_continuous(limits = c(697046-100, 700829 + 300))+
  annotate("text", x = 697225,y = 599750, label = "B.", size = 10)+
  annotation_scale(location = "br", 
                   pad_x = unit(0.75, "cm"),
                   pad_y = unit(0.8, "cm"))+
  annotation_north_arrow(location = "br", 
                   pad_x = unit(0.80, "cm"),
                   pad_y = unit(1.25, "cm"),
                   style = north_arrow_orienteering())+
  theme_minimal() + 
  theme(legend.position = "none",
        legend.direction = "vertical",
        legend.box = "horizontal",
        legend.key.height = unit(.5, 'cm'), 
        legend.background = element_rect(color = "black",
                                         fill = alpha("white", .75)),
        axis.title = element_blank(),
        axis.text = element_blank(), 
        panel.grid = element_blank(),
        panel.border = element_rect(fill =NA))

Fig2b_leg <- as_ggplot(get_legend(Fig2b + theme(legend.position = "top")))

```

## C

```{r fig2.C}

Fig2c <- base+
  guides(fill="none")+
  geom_point(data = assemblages, aes(x = Easting, y = Northing, size = n_hammer), inherit.aes = FALSE) +
  scale_color_manual(values = rock_colors) + 
  coord_equal()+
  labs(size = "N Hammers") + 
  scale_y_continuous(limits = c(596400-300, 599268 + 700))+
  scale_x_continuous(limits = c(697046-100, 700829 + 300))+
  annotate("text", x = 697225,y = 599750, label = "C.", size = 10)+
  annotation_scale(location = "br", 
                   pad_x = unit(0.75, "cm"),
                   pad_y = unit(0.8, "cm"))+
  annotation_north_arrow(location = "br", 
                   pad_x = unit(0.80, "cm"),
                   pad_y = unit(1.25, "cm"),
                   style = north_arrow_orienteering())+
  theme_minimal() + 
  theme(legend.position = "none",
        legend.direction = "vertical",
        legend.box = "horizontal",
        legend.key.height = unit(.5, 'cm'), 
        legend.background = element_rect(color = "black",
                                         fill = alpha("white", .75)),
        axis.title = element_blank(),
        axis.text = element_blank(), 
        panel.grid = element_blank(),
        panel.border = element_rect(fill =NA))


Fig2c_leg <- as_ggplot(get_legend(Fig2c + theme(legend.position = "left"), position = "left"))

```

## Final Figure 2

```{r, fig.height=14, fig.width=28}

fig.2 <- egg::ggarrange(Fig2a,Fig2b,Fig2c,Fig2a_leg,Fig2b_leg,Fig2c_leg, ncol = 3, nrow=2)

```


# Statistical Analyses

## Rebound Hardness
```{r}

# Test for normality 
rb_shap <- shapiro.test(djr_rbh$Hardness_Value) # Not Normal

# Kruskal Wallis
rb_kw_res <- kruskal.test(djr_rbh$Hardness_Value,djr_rbh$Material)

# Post Hoc Test

rb_ph_res <- FSA::dunnTest(djr_rbh$Hardness_Value,djr_rbh$Material)

```


## Artifact Density Model

```{r}
full_model <- glm(formula = n_stone_no_anvil~SPECIES + primary_rm + stone_anvil_present, family = "poisson", data = xdata)
```

### Check for Overdispersion 

```{r}
performance::check_overdispersion(full_model)
```

The model is over dispersed. Use a negative binomial model. 

### Negative Binomial Model
```{r}

full_model <- glm.nb(n_stone_no_anvil~SPECIES + primary_rm + stone_anvil_present, data = xdata)

```

###Check for Overdispersion 

```{r}

performance::check_overdispersion(full_model)

```

Negative binomial model sorts the issue. 

### Check for collinearity 

```{r}

library(car)

xx <- lm(n_stone_no_anvil~SPECIES + primary_rm + stone_anvil_present, data = xdata)

vif(xx)

```

### Full-Null model comparison

```{r}

null <- glm.nb(formula = n~1, data = xdata)

fn_res <- anova(null, full_model, test = "Chisq")

```

Analysis of deviance reveals the model is significant.

### Summary of Model

```{r}
xres <- summary(full_model)
xres
```

### Significance of individual variables

```{r}
drop1(full_model, test = "Chisq")
```


```{r fig3, fig.height=4, fig.width=12}

a <- ggplot(xdata[!is.na(xdata$SPECIES),], 
            aes(x = SPECIES, y = n_stone_no_anvil)) + 
  geom_boxplot()+
  ggtitle(label = "A.") + 
  labs(x="Species", y= "Number of Stones") + 
  theme(panel.background = element_rect(fill = NA, colour = "black"))

b <- ggplot(xdata, aes(x = primary_rm, y = n_stone_no_anvil)) + 
  geom_boxplot() + 
  ggtitle(label = "B.") + 
  labs(x="Primary Raw Material", y= "Number of Stones") +
  theme(panel.background = element_rect(fill = NA, colour = "black"))

c <- ggplot(xdata, aes(x = stone_anvil_present, y = n_stone_no_anvil)) + 
  geom_boxplot() + 
  ggtitle(label = "C.") + 
  labs(x="Stone Anvil Present", y= "Number of Stones") +
  theme(panel.background = element_rect(fill = NA, colour = "black"))

fig.3 = egg::ggarrange(a,b,c, ncol = 3)

```


## Number of Hammers Model

```{r}
full_model <- glm(formula = n_hammer~SPECIES + primary_rm + stone_anvil_present, family = "poisson", data = xdata)
```

### Check for Overdispersion 

```{r}
performance::check_overdispersion(full_model)
```

The model is over dispersed. Use a negative binomial model. 

### Negative Binomial Model
```{r}
full_model <- glm.nb(n_hammer~SPECIES + primary_rm + stone_anvil_present, data = xdata)
```

###Check for Overdispersion 
```{r}
performance::check_overdispersion(full_model)
```
Negative binomial model sorts the issue. 
### Check for collinearity 

```{r}

xx <- lm(n_hammer~SPECIES + primary_rm + stone_anvil_present, data = xdata)
vif(xx)

```
Coefficients with hardness are a bit unstable. 

### Full-Null model comparison

```{r}

null <- glm.nb(formula = n_hammer~1, data = xdata)

fn_res <- anova(null, full_model, test = "Chisq")

```

Analysis of deviance reveals the model is significant.

### Summary of Model

```{r}

xres <- summary(full_model)
xres
```

### Significance of individual variables
```{r}
drop1(full_model, test = "Chisq")
```

```{r fig4, fig.height=4, fig.width=12}

ylab <- "Number of Hammers"

a <- ggplot(xdata[!is.na(xdata$SPECIES),], 
            aes(x = SPECIES, y = n_hammer)) + 
  geom_boxplot() + 
  ggtitle(label = "A.") + 
  labs(x="Species", y= "Number of Hammers") + 
  theme(panel.background = element_rect(fill = NA, colour = "black"))

b <- ggplot(xdata[!is.na(xdata$primary_rm),], aes(x = primary_rm, y = n_hammer)) + 
  geom_boxplot() + 
  ggtitle(label = "B.") + 
    labs(x="Primary Raw Material", y= "Number of Hammers") + 
  theme(panel.background = element_rect(fill = NA, colour = "black"))

c <- ggplot(xdata, aes(x = stone_anvil_present, y = n_hammer)) + 
  geom_boxplot() + 
  ggtitle(label = "C.") + 
  labs(x="Stone Anvil Present", y= "Number of Hammers") + 
  theme(panel.background = element_rect(fill = NA, colour = "black"))
  

fig.4 <- egg::ggarrange(a,b,c, ncol = 3)

```


## Max Artifact Size

```{r}

full_model <- glm(formula =max_weight~SPECIES + primary_rm + stone_anvil_present, family = "gaussian", data = xdata[xdata$Square != "PrQL-42",])
```


```{r}

xx <- lm(max_weight~SPECIES + primary_rm + stone_anvil_present, data = xdata[xdata$Square != "PrQL-42",])
vif(xx)

```

### Full-Null model comparison

```{r}

null <- glm(formula = max_weight~1, family = "gaussian", data = xdata[xdata$Square != "PrQL-42",])

fn_res <- anova(null, full_model, test = "Chisq")

```

Analysis of deviance reveals the model is significant.

### Summary of Model

```{r}
xres <- summary(full_model)
```

### Significance of individual variables
```{r}
drop1(full_model, test = "Chisq")
```

```{r SOM Fig 4,  fig.height=4, fig.width=12}

a <- ggplot(xdata[!is.na(xdata$SPECIES),], 
            aes(x = SPECIES, y = as.numeric(max_weight))) + 
  geom_boxplot() + 
  ggtitle(label = "A.") + 
  labs(x="Species", y= "Max Weight") + 
  theme(panel.background = element_rect(fill = NA, colour = "black"))
  

b <- ggplot(xdata[!is.na(xdata$primary_rm),], aes(x = primary_rm, y = max_weight)) +
  geom_boxplot() + 
  ggtitle(label = "B.") + 
  labs(x="Primary Material", y= "Max Weight") + 
  theme(panel.background = element_rect(fill = NA, colour = "black"))


c <- ggplot(xdata, aes(x = stone_anvil_present, y = as.numeric(max_weight))) +
  geom_boxplot() +
  ggtitle(label = "C.") + 
  labs(x="Stone Anvil Present", y= "Max Weight") + 
  theme(panel.background = element_rect(fill = NA, colour = "black"))

SOM.fig.4 = egg::ggarrange(a,b,c, ncol = 3)

SOM.fig.4
```


